---
title: "ecoidx"
output: 
  github_document:
    html_preview: true
    df_print: tibble # kable # tibble
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = T,
  fig.path = "man/figures/")

devtools::load_all()
```

This R package consists of a set of helper datasets and plotting functions for developing and communicating marine ecological indicators, particularly for NOAA's Integrated Ecological Assessment program in the California Current.

## Load the R package

This package lives on Github, not yet CRAN, so you'll need to run the following once:

```{r, eval=F}
remotes::install_github("marinebon/ecoidx")
```

Then to load the package when using:

```{r}
library(ecoidx)
```

## Datasets

Most datasets were loaded from [ERDDAP searching "cciea"](https://oceanview.pfeg.noaa.gov/erddap/search/index.html?page=1&itemsPerPage=1000&searchFor=cciea).

You can see the available datasets for this package from the R Console with:

```{r}
data(package = "ecoidx")
```

Or look at the [Reference](./reference/index.html#section-datasets-erddap).

The ERDDAP datasets are "evergreen" and preferred. These are loaded for convenience, especially for quickly trying out the data wrangling and plotting functions.

## Plotting

You can also embed plots, for example:

```{r}
# example time series dataset
ts1

# defaults to include all options
g <- plot_ts(ts1)
g
cat(attr(g, "caption"))

# without SElo or SEhi
g <- plot_ts(ts1[,c("year","index")])
g
cat(attr(g, "caption"))

# without x_recent, add_avg, add_icons
g <- plot_ts(ts1, x_recent=NA, add_icons=F, add_avg=F)
g
cat(attr(g, "caption")) # empty caption without x_recent
```

## Developer

### One time

Setup Github Actions to update documentation upon `git push` into `gh-pages` branch:

```r
usethis::use_github_action("pkgdown")
```

Modified the [.github/workflows/pkgdown.yaml](https://github.com/marinebon/ecoidx/blame/5b1b44104029fbc167146b9037b0030db390f774/.github/workflows/pkgdown.yaml#L38-L50) with 3 extra lines to fully document the package from source:

```yaml
    - name: Install dependencies
      ...
          install.packages("devtools", type = "binary")
    - name: Deploy package
      ...
          Rscript -e 'devtools::document()'
          Rscript -e 'rmarkdown::render("README.Rmd")'
```

### Load dataset

1. Place into CSV into `data-raw/` folder
1. Create dataset. Create `get_[dataset].R` script to read, potentially wrangle and then load into R package as a dataset using `usethis::use_data()`. Run `get_[dataset].R` to generate `data/[dataset].rda`.
1. Document dataset. Create `R/[dataset].R`. Run `devtools::document()` to create `man/[dataset].Rd`.
1. Document package. Run `pkgdown::build_reference()` to update `docs/reference/index.html`.

### Develop functions

To import a library:

```r
usethis::use_package("dplyr")
usethis::use_package("ggplot2")
```

After updating documentation:

```r
devtools::document()
pkgdown::build_reference()
```
